Gaia DR2 view of the GD-1 stellar stream

### 2018-04-26 paper/gd1.tex
regroup results
plot and notebooks

% typography
\setlength{\parindent}{1.\baselineskip}
% \newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\package}[1]{\textsl{#1}}

@@

@@

\subsection{Density along the stream}
\label{sec:density}

\subsection{Kinematic profile}
\label{sec:kinematics}

@@

\acknowledgements{
thanks: Casey, Geha, Hogg, Spergel
CCA for hospitality
AB acknowledges generous support from the Institute for Theory and Computation at Harvard University.
All code used in this work and all results are available at \url{https://github.com/adrn/GD1-DR2}.
}

@@

>>>>

% typography
\setlength{\parindent}{1.\baselineskip}
% \newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\package}[1]{\textsl{#1}}
\newcommand{\gaia}{\textsl{Gaia}}

@@

(\citealt{Schlegel:1998, Schlafly:2011}; hereafter SFD)

Maximum $A_G$ is $\approx$0.07 mag in both the under-density and gap regions.

% Notebook: GD1-dust-and-completeness
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{sfd.pdf}
\end{center}
\caption{%
Colored background shows the \gaia\ $G$-band extinction, $A_G$, in the GD-1
coordinate system.
Vertical lines roughly show the regions identified as the under-density (UD) and
gap.
The maximum extinction in the UD or Gap regions is $\approx$0.07 mag.
\label{fig:sfd}
}
\end{figure}

@@

\subsection{Global properties}
\label{sec:res_global}

\subsection{Gap}
\label{sec:res_gap}

\subsection{Underdensity}
\label{sec:res_underdensity}

@@

\acknowledgements{
thanks: Casey, Geha, Hogg, Spergel, Koposov
CCA for hospitality
AB acknowledges generous support from the Institute for Theory and Computation at Harvard University.
All code used in this work and all results are available at \url{https://github.com/adrn/GD1-DR2}.
}

@@

\clearpage

\appendix
\section{Completeness check and data validation}
\label{sec:validate}

% % Notebook:
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=0.7\textwidth]{nvisits.pdf}
% \end{center}
% \caption{%
% TODO
% \label{fig:TODO}
% }
% \end{figure}
